Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-25 docs/thesis/appendix-test_equations.tex
work on thesis: finished sample equations

\\
\hline
Eq1 & \scriptsize{ Time-independent Schr\char"00F6dinger equation} & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>$\nabla$</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>=</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & \scriptsize{ $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ }\\ \hline

Eq2 & \scriptsize{Atomic mass in terms of number of proton and number of neutrons} & \scriptsize {\codefont <math> <mi>A</mi> <mo>=</mo> <mi>Z</mi> <mo>+</mo> <mi>N</mi> </math>} & \scriptsize{$A = Z + N$} \\ \hline

Eq3 & \scriptsize{Radiation flux in term of the initial intensity, the absorption coefficient and the thickness of a substance} & \scriptsize {\codefont <math> <mi>I</mi> <mo>=</mo> <msub> <mi>I</mi> <mn>0</mn> </msub><msup> <mi>e</mi> <mrow> <mo>-</mo> <mi>μ</mi> <mi>x</mi> </mrow> </msup> </math>
} & \scriptsize{$I = I_0e^{-\mu x}$ } \\ \hline

Eq4 & \scriptsize{Higgs Boson decaying process into $W^+$ and $W^-$ bosons. This is not exactly a mathematical equation, but a physical process. However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \scriptsize{$H\rightarrow W^+W^-$ } \\ \hline

Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math> <msub> <mi>G</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <msub> <mi>R</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mi>R</mi> <msub> <mi>g</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <mfrac> <mrow> <mn>8</mn> <mi>π</mi> <mi>G</mi> </mrow> <msup> <mi>c</mi> <mn>4</mn> </msup> </mfrac> <msub> <mi>T</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> </math>
 </math>
 } & \scriptsize{$G_{\mu\nu}\equiv R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline

Eq6 & \scriptsize{Luminosity of a star in terms of its temperature and radius} & \scriptsize {\codefont <math><mi>L</mi><mo>=</mo><mn>4</mn><mi>π</mi><msup><mi>R</mi><mn>2</mn></msup><mi>σ</mi><msubsup><mi>T</mi><mrow><mi>e</mi><mi>f</mi><mi>f</mi></mrow><mn>4</mn></msubsup></math>
} & \scriptsize{$ L = 4\piR^2\sigma T^4_{eff} $ } \\ \hline

>>>>

\\
\hline
Eq1 & \scriptsize{ Time-independent Schr\char"00F6dinger equation} & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>$\nabla$</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>=</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & \small{ $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ }\\ \hline

Eq2 & \scriptsize{Atomic mass in terms of number of proton and number of neutrons} & \scriptsize {\codefont <math> <mi>A</mi> <mo>=</mo> <mi>Z</mi> <mo>+</mo> <mi>N</mi> </math>} & \small{$A = Z + N$} \\ \hline

Eq3 & \scriptsize{Radiation flux in term of the initial intensity, the absorption coefficient and the thickness of a substance} & \scriptsize {\codefont <math> <mi>I</mi> <mo>=</mo> <msub> <mi>I</mi> <mn>0</mn> </msub><msup> <mi>e</mi> <mrow> <mo>-</mo> <mi>μ</mi> <mi>x</mi> </mrow> </msup> </math>
} & \small{$I = I_0e^{-\mu x}$ } \\ \hline

Eq4 & \scriptsize{Higgs Boson decaying process into $W^+$ and $W^-$ bosons. This is not exactly a mathematical equation, but a physical process. However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \small{$H\rightarrow W^+W^-$ } \\ \hline

Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math> <msub> <mi>G</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <msub> <mi>R</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mi>R</mi> <msub> <mi>g</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <mfrac> <mrow> <mn>8</mn> <mi>π</mi> <mi>G</mi> </mrow> <msup> <mi>c</mi> <mn>4</mn> </msup> </mfrac> <msub> <mi>T</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> </math>
 </math>
 } & \footnotesize{$G_{\mu\nu} = R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline

Eq6 & \scriptsize{Luminosity of a star in terms of its temperature and radius} & \scriptsize {\codefont <math> <mi>L</mi> <mo>=</mo> <mn>4</mn> <mi>π</mi> <msup> <mi>R</mi> <mn>2</mn> </msup> <mi>σ</mi> <msubsup> <mi>T</mi> <mrow> <mi>e</mi> <mi>f</mi> <mi>f</mi> </mrow> <mn>4</mn> </msubsup> </math>
} & \small{$ L = 4 \pi R^2 \sigma T^4_{eff} $ } \\ \hline

Eq7 & \scriptsize{Free-cyclotron motion of an electron in terms of its charge, mass and the magnetic field} & \scriptsize {\codefont <math> <msub> <mi>ω</mi> <mi>c</mi> </msub> <mo>=</mo> <mo>|</mo> <mi>q</mi> <mover accent="true"> <mi>B</mi> <mo>→</mo> </mover> <mo>|</mo> <mo>/</mo> <mi>m</mi> </math>
} & \small{$ \omega_c = |q\vec{B}|/m $ } \\ \hline

Eq8 & \scriptsize{Spin energy of a particle in presence of an external magnetic field} & \scriptsize{\codefont <math> <mi>E</mi> <mo>=</mo> <mo>-</mo> <mover accent="true"> <mi>μ</mi> <mo>→</mo> </mover> <mo>⋅</mo> <mover accent="true"> <mi>B</mi> <mo>→</mo> </mover> </math>
} & \small { $E = -\vec{\mu} \cdot \vec{B}$ } \\ \hline

Eq9 & \scriptsize{Quantum electrodynamics Lagrangian modelling the interaction of the -1/2 spin field with the electromagnetic field} & \scriptsize{\codefont <math > <msub> <mi mathvariant="script">L</mi> <mstyle mathvariant="normal"> <mi>Q</mi> <mi>E</mi> <mi>D</mi> </mstyle> </msub> <mo>=</mo> <msub> <mover accent="true"> <mi>ψ</mi> <mo>̄</mo> </mover> <mi>i</mi> </msub> <mi>i</mi> <mfenced close=")" open="("> <mrow> <msub> <mfenced close=")" open="("> <mrow> <msup> <mi>γ</mi> <mi>μ</mi> </msup> <msub> <mi>D</mi> <mi>μ</mi> </msub> </mrow> </mfenced> <mrow> <mi>i</mi> <mi>j</mi> </mrow> </msub> <mo>-</mo> <mi>m</mi> <msub> <mi>δ</mi> <mrow> <mi>i</mi> <mi>j</mi> </mrow> </msub> </mrow> </mfenced> <msub> <mi>ψ</mi> <mi>j</mi> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <msub> <mi>F</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <msup> <mi>F</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msup> </math>
} & \small { $\mathcal{L}_\mathrm{QED} 
= \bar{\psi}_i i \left( (\gamma^\mu D_\mu)_{ij} - m\, \delta_{ij}\right) \psi_j - \frac{1}{4}F_{\mu \nu} F^{\mu \nu}  $ } \\ \hline

Eq10 & \scriptsize{Einstein-Hilbert action} & \scriptsize{\codefont <math> <mi>S</mi> <mo>=</mo> <mfrac> <mn>1</mn> <mrow> <mn>2</mn> <mi>κ</mi> </mrow> </mfrac> <mo>∫</mo> <mi>R</mi> <msqrt> <mrow> <mo>-</mo> <mi>g</mi> </mrow> </msqrt> <msup> <mi>d</mi> <mn>4</mn> </msup> <mi>x</mi> </math>} & \small { $ 
    S = {1 \over 2\kappa} \int R \sqrt{-g} \, \mathrm{d}^4x	$ } \\ \hline

### 2014-02-25 docs/thesis/chap-cern_math_explorer.tex
work on thesis: finished sample equations

\subsubsection{Specific domain structures}
Additionally, we identified patterns that are relevant and frequent in specific domains of the high energy physics. Some patterns can be as general as a derivative over time ($dx/dt$), or more specific ones like a particle decaying process ($originalParticle \rightarrow subparticle1, subparticle2, subparticle3$) and some in the middle like the general structure of a given action: $S = \int^{t2}_{t1} \mathcal{L} dt$. The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns.

>>>>

\subsubsection{Specific domain structures}

Additionally, there are common patterns to specific domains which can improve the quality of the retrieved results. Some specific patterns we identified include: $originalParticle \rightarrow subparticle1, subparticle2, subparticle3$ (For representing particle decaying processes) $S = \int^{t2}_{t1} \mathcal{L} dt$ (For an action in terms of its Lagrangian) and $SU(n)$ (For describing special unitary groups). The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns and for this reason we did not tried to do an exhaustive list of them.
